% LaTeX resume using res.cls
\documentclass[line,margin]{res} 

% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 

% \usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\begin{document}

\name{\Huge{Bruno Croci}}

\address{Düsseldorf - Germany}
\address{bruno@croci.me - \href{https://bruno.croci.me/}{https://bruno.croci.me/}}

 
\begin{resume}
 
  \section{SUMMARY} A seasoned generalist programmer with a passion for creating experiences and building robust systems. 15+ years of experience spanning gameplay, audio, and tools development, with a track record of delivering impactful features for AAA, VR, mobile and online games. Specializing in C++, C\#, Javascript, and a deep understanding of systems programming, web and audio pipelines.
 
\section{EXPERIENCE} 
        {\sl Senior Audio Programmer} \hfill 11/2022 - current \\
        {\sl Programmer} \hfill 04/2020 - 11/2022 \\
                Ubisoft Düsseldorf, Düsseldorf, Germany
        \begin{itemize}  \itemsep 1.25pt
            \item Audio systems development for AC Nexus, XDefiant and other unannounced titles, such as VO pipeline, sound propagation, emitter management, etc.
            \item Creating audio tools to support Audio Designers, bridging the middleware Wwise with in-house engine Snowdrop and implementing new features in the engine.
            \item Maintain the base AI code for NPCs in the Assassin's Creed Nexus game.
            \item Implement tools for animators to have more control when implementing NPCs behaviors animations.
            \item Developing prototypes for features and possible games with owned IPs.
            \item Keywords: C++, C\#, Snowdrop, Wwise, Behavior Trees, AI Programming.
        \end{itemize}

        {\sl Software Developer} \hfill 01/2019 - 03/2020 \\
		Touch Press Inc., Dublin, Ireland
        \begin{itemize}  \itemsep 1.25pt
            \item Main developer maintaining Hungry Caterpillar\texttrademark  Play School., an educational app for children.
            \item Collaborate with learning designers to add new content to the app.
            \item Optimizing the pipeline to improve the quality of life of designers and artists, from contribution to deploy.
            \item Implementing new features for future activities and mini-games.
            \item Maintaining the subscription system and implementing campaigns.
            \item Keywords: C\#, Unity, Android, iOS, AWS.
        \end{itemize}

        {\sl Senior Game Engineer} \hfill 04/2017 - 01/2019 \\
        {\sl Game Developer} \hfill 02/2014 - 03/2017 \\
                Samsung Electronics / Black River Studios, Manaus, Brazil
        \begin{itemize}  \itemsep 1.25pt
            \item As a first-party Samsung game studio, our goal was to showcase new technologies and devices.
            \item Wrote the ballistic system for Conflit0: Shattered, a VR shooter game.
            \item Ported Conflict0: Revolution from Tizen to Android and implemented the systems to support the new history DLC.
            \item Building the initial game architecture in Finding Monsters Adventures, a mobile and VR photography game. Based on a custom pubsub broker to have all the game systems communicate. Also other systems such as achievements and missions.
            \item Implementation of a full backend service for Galaxy11: Invation, a mobile runner game made to demonstrate the power of Samsung Galaxy S4. RESTful API to store player profiles and leaderboards written in Python with Flask, using MySQL and Redis.
            \item Keywords: C\#, Unity, VR, GearVR, Windows Mixed Reality, Tizen.
        \end{itemize}
                 
        {\sl Game Developer} \hfill 11/2011 - 01/2014 \\
                Hive Digital Media, São Paulo, Brazil
        \begin{itemize}  \itemsep 1.25pt
            \item Implemented Playboy Poker, a licensed online poker game targeting the Latin America market, that ran on Facebook. I wrote all the client code in AS3 (Flash), and a big part of the server in Java using SmartFoxServer.
            \item Later I ported that project into another licensed poker game (this time for a local sports TV). I was responsible for the full port as well as maintaining the integrations between the real-time server and the user registration system (written in PHP).
            \item Implemented Tako Kamis, a game inspired by My Brute and Pokémon, for the SmartTV LG platform. I also implemented the server side Rest API (in PHP with Zend Framework) that controlled the whole game, including multiplayer matches, battle logic and user registration code.
            \item Keywords: Flash, AS3, Unity, C\#, Javascript, Android, iOS, Java.
        \end{itemize}
                 
        {\sl Game Programmer} \hfill 09/2010 - 11/2011 \\
                Loopix Digital Group, São Paulo, Brazil
        \begin{itemize}  \itemsep 1.25pt
                \item Game development with Flash and AS3.
                \item Concept and implementation of communication protocols to integrate games with the platform. 
                \item Keywords: C\#, AS3, Java, Javascript.
        \end{itemize}
 
        {\sl Web Developer} \hfill 01/2009 - 10/2009 \\
                Detetive.net, São Paulo, SP, Brazil
        \begin{itemize}  \itemsep 1.25pt
                \item Full-stack development of a photo sharing social network.
                \item Keywords: PHP, CSS, HTML, Javascript.
        \end{itemize} 

\section{FORMAL EDUCATION}
        {\sl Computer Science Technician} \\
                Colégio Eniac - São Paulo \\
                conclusion: 2008
                
\section{RELEVANT\\PERSONAL\\PROJECTS}   
        \begin{itemize}  \itemsep 1.25pt
            \item \href{https://github.com/CrociDB/annileen}{\textbf{annileen}}: A toy 3D game engine made in C++ using BGFX as a graphics backend. Tooling is mostly in Python.
            \item \href{https://github.com/CrociDB/bulletty}{\textbf{bulletty}}: A TUI feed reader written in Rust.
            \item \href{https://github.com/CrociDB/flingern}{\textbf{flingern}}: Art gallery static website generator written in Python. It powers my art website.
            \item \href{https://github.com/CrociDB/wordlos}{\textbf{WORLDOS}}: Clone of the neo-classic WORLDE game for DOS, written in x86 16bit Assembly.
        \end{itemize} 


\section{ADDITIONAL \\ INFORMATION}
        \begin{itemize}  \itemsep 1pt
                \item Linkedin profile: \href{https://www.linkedin.com/in/crocidb}{https://www.linkedin.com/in/crocidb}
                \item Github profile with code samples: \href{http://github.com/CrociDB}{http://github.com/CrociDB}
                \item Personal Blog: \href{http://crocidb.com/}{http://crocidb.com/}
        \end{itemize} 

\end{resume}
\end{document}
